\plaintitle

### 2016-07-16 drafts/labor/trackingWork.tex
various intro revs

\usepackage{todonotes,txfonts,balance,graphics,color,alphalph,subfiles}
\usepackage{booktabs,textcomp,microtype,ccicons,enumitem,moreenum,nth}
\usepackage[normalem]{ulem}
\usepackage[citestyle=numeric,backend=bibtex,bibencoding=ascii]{biblatex}
\usepackage[T1]{fontenc}
\usepackage[pdftex,pdfpagelabels=false]{hyperref}
\usepackage[all]{hypcap}  % Fixes bug in hyperref caption linking
\usepackage[utf8]{inputenc} % for a UTF8 editor only

@@

% create a shortcut to typeset table headings
% \newcommand\tabhead[1]{\small\textbf{#1}}
\bibliography{../../../../references}

@@

The HCI community is perhaps most familiar with examples of task--based work such as
99designs,
Amazon Mechanical Turk (AMT),
and increasingly
Uber \& Lyft,
which all allow requesters in various forms to tap into
resources such as
cars,
computers, and above all
``cognitive surplus''
with relative ease
\cite{howe2006rise,DillahuntPromise,storiesIraniSilberman,shirky2010cognitive}.
This insight, that
workers can be geographically distributed and tasks decomposed,
% (especially given careful central management of those workers, discussed later),
has proven remarkably compelling
and an effective fulcrum for leveraging the Internet for highly scalable work
\cite{sensitiveTasks,embracingErrorKrishna}.

>>>>

\usepackage{todonotes,txfonts,balance,graphics,color,alphalph,subfiles}
\usepackage{booktabs,textcomp,microtype,ccicons,enumitem,moreenum,nth}
\usepackage[normalem]{ulem}
% \usepackage[citestyle=numeric,backend=bibtex,bibencoding=ascii]{biblatex}
\usepackage{biblatex}
\usepackage[T1]{fontenc}
\usepackage[pdftex,pdfpagelabels=false]{hyperref}
\usepackage[all]{hypcap}  % Fixes bug in hyperref caption linking
\usepackage[utf8]{inputenc} % for a UTF8 editor only

@@

% create a shortcut to typeset table headings
% \newcommand\tabhead[1]{\small\textbf{#1}}
\bibliography{references}

@@

\cite{olson2014ways}
The HCI community is perhaps most familiar with examples of task--based work such as
99designs,
Amazon Mechanical Turk (AMT),
and increasingly
Uber \& Lyft,
which all allow requesters in various forms to tap into
resources such as
cars,
computers, and above all
``cognitive surplus''
with relative ease
\cite{howe2006rise,DillahuntPromise,storiesIraniSilberman,shirky2010cognitive}.
This insight, that
workers can be geographically distributed and tasks decomposed,
% (especially given careful central management of those workers, discussed later),
has proven remarkably compelling
and an effective fulcrum for leveraging the Internet for highly scalable work
\cite{sensitiveTasks,embracingErrorKrishna}.
